Deeply Integrating C11 Code Support into Isabelle/PIDE

### 2019-10-22 C11-FrontEnd/document/generated/paper.tex
added ref to FIDE paper

  Our approach demonstrates the degree of maturity and expressive power the Isabelle/PIDE subsystem
  has achieved in recent years. Our integration technique employs Lex and Yacc style grammars to 
  ensure efficient deterministic parsing. We present two case studies for the integration of 
  (known) semantic back-ends in order to validate the design decisions for our
  back-end interface.%
\end{isamarkuptext*}\isamarkuptrue%
%
\begin{isamarkupsection*}%
[label = {intro},type = {scholarly_paper.introduction}, args={label = {intro},type = {scholarly_paper.introduction}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}}]Introduction%
\end{isamarkupsection*}\isamarkuptrue%
%
\begin{isamarkuptext*}%
[label = {introtext},type = {scholarly_paper.introduction}, args={label = {introtext},type = {scholarly_paper.introduction}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}}]\noindent{}Recent successes like the Microsoft Hypervisor project \cite{DBLP:conf/fm/LeinenbachS09},
the verified CompCert compiler \cite{DBLP:journals/cacm/Leroy09}
and the seL4 microkernel \cite{DBLP:conf/sosp/KleinEHACDEEKNSTW09,DBLP:journals/tocs/KleinAEMSKH14} 
show that the verification of low-level systems code has become feasible.
However, a closer look at the underlying verification engines  
VCC \cite{DBLP:conf/tphol/CohenDHLMSST09}, 
or Isabelle/AutoCorres \cite{DBLP:conf/pldi/GreenawayLAK14}
show that the road is still bumpy: the  empirical cost evaluation  of the L4.verified project 
\cite{DBLP:journals/tocs/KleinAEMSKH14} reveals that a very substantial part  of the overall 
effort of about one third of the 28 man years went into the development of libraries and the 
associated tool-chain. Accordingly, the project authors \cite{DBLP:journals/tocs/KleinAEMSKH14} 
express the hope that these overall investments will not have to be repeated for 
``similar projects''.

>>>>

  Our approach demonstrates the degree of maturity and expressive power the Isabelle/PIDE subsystem
  has achieved in recent years. Our integration technique employs Lex and Yacc style grammars to 
  ensure efficient deterministic parsing. We present two case studies for the integration of 
  (known) semantic back-ends in order to validate the design decisions for our
  back-end interface.

  \textbf{In case that you consider citing Isabelle/C, please refer to \cite{Tuong-IsabelleC:2019}.  } %
\end{isamarkuptext*}\isamarkuptrue%
%
\begin{isamarkupsection*}%
[label = {intro},type = {scholarly_paper.introduction}, args={label = {intro},type = {scholarly_paper.introduction}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}}]Introduction%
\end{isamarkupsection*}\isamarkuptrue%
%
\begin{isamarkuptext*}%
[label = {introtext},type = {scholarly_paper.introduction}, args={label = {introtext},type = {scholarly_paper.introduction}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}}]\noindent{}Recent successes like the Microsoft Hypervisor project \cite{DBLP:conf/fm/LeinenbachS09},
the verified CompCert compiler \cite{DBLP:journals/cacm/Leroy09}
and the seL4 microkernel \cite{DBLP:conf/sosp/KleinEHACDEEKNSTW09,DBLP:journals/tocs/KleinAEMSKH14} 
show that the verification of low-level systems code has become feasible.
However, a closer look at the underlying verification engines  
VCC \cite{DBLP:conf/tphol/CohenDHLMSST09}, 
or Isabelle/AutoCorres \cite{DBLP:conf/pldi/GreenawayLAK14}
show that the road is still bumpy: the  empirical cost evaluation  of the L4.verified project 
\cite{DBLP:journals/tocs/KleinAEMSKH14} reveals that a very substantial part  of the overall 
effort of about one third of the 28 man years went into the development of libraries and the 
associated tool-chain. Accordingly, the project authors \cite{DBLP:journals/tocs/KleinAEMSKH14} 
express the hope that these overall investments will not have to be repeated for 
``similar projects''.
